Figures for conference paper

### 2019-04-25 conference figures.Rmd
align the two input clusters

      # Input Data
      subgraph cluster0 {
      label = 'Input Data';
      style = filled;
		  color = lightgrey;
		  node [style = filled, color = black, fillcolor = white];
      CD [label = 'Course Data']
      SD [label = 'Student Data']
      }

      # User Input
      subgraph cluster1 {
      label = 'User Input';
      style = filled;
		  color = coral;
		  node [style = filled, color = black, fillcolor = white];
      ID [label = 'Student ID']
      KW [label = 'Selected Key Words']
      CS [label = 'Selected Courses']
      }

      # Ouput
      subgraph cluster2 {
      label = 'System Output';
      style = filled;
		  color = lightCyan;
		  node [style = filled, color = black, fillcolor = white];
      rank = same;
      SUG [label = 'Course Suggestions']
      WAR [label = 'Warnings']
      PRE [label = 'Preparatory Coursework']
      }

      # Intermediate nodes
      node [color = black]
      TM [label = 'Topic Model']
      TE [label = 'Student큦 Topic Expertise']
      AI [label = 'Student큦 Academic Interests']
      AP [label = 'Student큦 Academic Performance']
      PM [label = 'Predictive Models']
      GP [label = 'Grade Prediction']
      TR [label = 'Student큦 Transcript']
      x [shape=circle,width=.01,height=.01,label='']

@@

      WAR SUG PRE [ group = 1 ]

      {TE, KW} -> AI; 
      {ID, SD} -> TR;
      TR -> AP;
      {TR, TM} -> TE;
      {PM, TE, AP, CS} -> GP;
      GP -> WAR;
		  {TM, PM, WAR} -> PRE;

@@

      edge[label = 'Lasso']
      SD -> PM;

      edge[label = '']
      {TM, AI} -> x [arrowhead=none]
      edge[label = 'KL distance', decorate = TRUE]
      x -> SUG;

>>>>

      subgraph cluster_input {
      label = '';
      style = filled;
		  color = white;

      subgraph cluster_input_data {
      label = 'Data';
      style = filled;
		  color = lightgrey;
		  node [style = filled, color = black, fillcolor = white];
      CD [label = 'Course Data']
      SD [label = 'Student Data']
      }

      subgraph cluster_input_user {
      label = 'User Input';
      style = filled;
		  color = coral;
		  node [style = filled, color = black, fillcolor = white];
      ID [label = 'Student ID']
      KW [label = 'Selected Key Words']
      CS [label = 'Selected Courses']
      }

      }

      subgraph cluster_inter_first{
      label = '';
      style = filled;
		  color = white;
      TE [label = 'Topic Expertise']
      AP [label = 'Academic Performance']
      }

      subgraph cluster_inter_last{
      label = '';
      style = filled;
		  color = white;
      GP [label = 'Grade Prediction']
      AI [label = 'Student´s Academic Interests']
      }

      # Ouput
      subgraph cluster_ouput {
      label = 'System Output';
      style = filled;
		  color = lightCyan;
		  node [style = filled, color = black, fillcolor = white];
      rank = same;
      SUG [label = 'Course Suggestions']
      WAR [label = 'Warnings']
      PRE [label = 'Preparatory Coursework']
      }

      # Intermediate nodes
      node [color = black]
      TM [label = 'Topic Model']
      PM [label = 'Predictive Models']
      TR [label = 'Student´s Transcript']

      # Invisible node
      node [shape = circle, width = .01, height = .01, label = '']
      x1 x2

@@

      SD -> AP;
      {SD, TM} -> TE;
      {TR, KW} -> AI;
      {ID, SD} -> TR;
      {PM, CS, TR} -> GP;
      GP -> WAR;
		  {TM, PM, WAR} -> PRE;

@@

      edge[label = '']
      {AP, TE} -> x2 [arrowhead = none]
      edge[label = ' Lasso', decorate = TRUE]
      x2 -> PM;

      edge[label = '']
      {TM, AI} -> x1 [arrowhead = none]
      edge[label = 'KL distance', decorate = TRUE]
      x1 -> SUG;
